### 2023-06-13 README.Rmd
230613_v0234sdfsfwrwer

<li><code>reach</code>: Inspired by the former
<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(buy at least one of the products) with your in the function determined
potential assortment. or the <code>method</code> argument you can decide
between <code>method = "threshold"</code> (if utility of product is
larger than the utility of <code>None</code>, it is marked as potential
purchase option) and <code>method = "First Choice"</code> (only product
with highest utility is considered. If its utility is above the utility
of <code>None</code>, it is marked as potential purchase option). If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>

>>>>

<li><code>reach</code>: Inspired by the former
<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. or the <code>method</code> argument you can decide
between <code>method = "threshold"</code> (if utility of product is
larger than the utility of <code>None</code>, it is marked as potential
purchase option) and <code>method = "First Choice"</code> (only product
with highest utility is considered. If its utility is above the utility
of <code>None</code>, it is marked as potential purchase option). If you
specify an optional <code>Group</code> argument the output is split by
groups.</li>
